My title

### 2024-11-04 paper/paper.qmd
Added paragraphs to introduction

Why it matters paragraph:

@@

@@

@@

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

# first_model <-
#   readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   statistic = "mad",
#   fmt = 2
# )
```

@@

The analysis utilizes Bayesian Generalized Linear Models (GLMs) and Monte Carlo simulations to estimate predicted support percentages for Kamala Harris and Donald Trump. With a win probability of 63.2% for Harris and 36.8% for Trump, the model suggests a modest advantage for Harris, albeit within a competitive margin. The density plot (Fig. 6) highlights the distributions of predicted support for both candidates, showing a slight overlap, which indicates close competition and underscores the uncertainty inherent in forecasting elections based on polling data.

>>>>

Utilizing Bayesian Generalized Linear Models (GLM) and Monte Carlo simulations to estimate the predicted support percentages for Kamala Harris and Donald Trump. Harris has a higher support percentage over Trump with a win probability of 63.2%, while Trump has a 36.8% win probability. The model suggest that although there is close competition between both candidates, Harris has an advantage based on the polling data.

Running the simulations for this data showcases the importance of state-level effects, support for each candidate varies significantly by region. The models indicate that Harris has strong support in traditionally Democratic states, whereas Trump maintains a lead in Republican-leading regions. Support for each candidate indicates that regional factors are pivotal in determining the final outcome for American elections.

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Plot distribution of predicted support for Harris
ggplot(data.frame(harris_pred_means), aes(x = harris_pred_means)) +
  geom_histogram(bins = 30, fill = "blue", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Predicted Support for Kamala Harris",
    x = "Predicted Support Percentage",
    y = "Frequency",
    caption = "Fig 4: This histogram shows the distribution of predicted support percentages\nfor Kamala Harris based on model simulations."
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.caption = element_text(size = 10, hjust = 0.5, margin = margin(t = 10))
  )

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Plot distribution of predicted support for Trump
ggplot(data.frame(trump_pred_means), aes(x = trump_pred_means)) +
  geom_histogram(bins = 30, fill = "red", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Predicted Support for Donald Trump",
    x = "Predicted Support Percentage",
    y = "Frequency", 
    caption = "Fig 5: This histogram shows the distribution of predicted support percentages\nfor Donald Trump based on model simulations."
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.caption = element_text(size = 10, hjust = 0.5, margin = margin(t = 10))
  )
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Determine the minimum length between the two prediction sets
min_length <- min(length(harris_pred_means), length(trump_pred_means))

# Subset both predictions to have the same length
harris_pred_means <- harris_pred_means[1:min_length]
trump_pred_means <- trump_pred_means[1:min_length]

# Combine predictions for comparison plot
comparison_data <- data.frame(
  support = c(harris_pred_means, trump_pred_means),
  candidate = rep(c("Harris", "Trump"), each = min_length)
)

# Plot comparison of support for Harris and Trump
ggplot(comparison_data, aes(x = support, fill = candidate)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Comparison of Predicted Support for Harris and Trump",
    x = "Predicted Support Percentage",
    y = "Density",
    fill = "Candidate",
    caption = "Fig 6: This density plot compares the predicted support percentages\n for Kamala Harris and Donald Trump based on model simulations."
  ) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_minimal(base_size = 14) +
  theme(
    plot.caption = element_text(size = 10, hjust = 0.5, margin = margin(t = 10))  # Adjust caption styling
  )

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Bayesian hierarchical model for Harris's support
harris_model <- stan_glm(
  percentage ~ pollster_name + sample_size + state,
  data = harris_data,
  family = gaussian(),
  prior = normal(0, 2.5, autoscale = TRUE),
  prior_intercept = normal(0, 2.5, autoscale = TRUE),
  seed = 853
)

# Generate posterior predictions for Harris' support
harris_pred <- posterior_predict(harris_model)
harris_pred_means <- colMeans(harris_pred)  # Mean predicted support across simulations

# Bayesian hierarchical model for Trump's support
trump_model <- stan_glm(
  percentage ~ pollster_name + sample_size + state,
  data = trump_data,
  family = gaussian(),
  prior = normal(0, 2.5, autoscale = TRUE),
  prior_intercept = normal(0, 2.5, autoscale = TRUE),
  seed = 853
)

# Generate posterior predictions for Trump's support
trump_pred <- posterior_predict(trump_model)
trump_pred_means <- colMeans(trump_pred)  # Mean predicted support across simulations

# Simulate election outcomes by comparing Harris and Trump's predicted support
simulated_outcomes <- ifelse(harris_pred_means > trump_pred_means, "Harris", "Trump")

# Calculate probabilities
harris_win_prob <- mean(simulated_outcomes == "Harris")
trump_win_prob <- mean(simulated_outcomes == "Trump")

# Print probabilities
cat("Probability Harris Wins:", harris_win_prob, "\n")
cat("Probability Trump Wins:", trump_win_prob, "\n")
```

@@

@@

The analysis utilizes Bayesian Generalized Linear Models (GLMs) and Monte Carlo simulations to estimate predicted support percentages for Kamala Harris and Donald Trump. With a win probability of 63.2% for Harris and 36.8% for Trump, the model suggests a modest advantage for Harris, albeit within a competitive margin. The density plot (Fig. 6) highlights the distributions of predicted support for both candidates, showing a slight overlap, which indicates close competition and shows the uncertainty inherent in forecasting elections based on polling data.
